### 2025-01-12 getting-started.qmd
20241016 - render the figure caption as alt text
20250112 - archived link

The following article provides additional resources and good guidance: <https://www.r-bloggers.com/where-to-get-help-with-your-r-question/>.

@@

![Types of merges/joins](images/joinTypes.png)

>>>>

The following article provides additional resources and good guidance: <https://www.r-bloggers.com/where-to-get-help-with-your-r-question/> (archived at <https://perma.cc/4RRE-KL33>).

@@

![Types of merges/joins](images/joinTypes.png)\
